### 2019-09-15 reports/thesis/chapters/2_dataCollection.tex
Change notation

For each power, the within and between pixel variance was calculated. Let $U_{x,y}^{(j)}(P)$ be the shading corrected greyscale image in the test set with power $P$ for $j=1,2,\dotsc,n$ replicates. The within and between pixel variance are
\begin{equation}
s_\mathrm{w}^2(P)=\dfrac{1}{WH(n-1)}
  \sum_{x=1}^{W}\sum_{y=1}^{H}\sum_{j=1}^{n}
  \left(
    U_{x,y}^{(j)}(P) - \overline{U}_{x,y}(P)
  \right)^2
\end{equation}
and
\begin{equation}
s_\mathrm{b}^2(P)=\dfrac{n}{WH-1}
  \sum_{x=1}^{W}\sum_{y=1}^{H}
  \left(
    \overline{U}_{x,y}(P) - \overline{U}(P)
  \right)^2
\end{equation}
respectively where
\begin{equation}
  \overline{U}_{x,y}(P) = \dfrac{1}{n}\sum_{j=1}^{n}U_{x,y}^{(j)}(P)
\end{equation}
and
\begin{equation}
  \overline{U}(P) = \dfrac{1}{WH}\sum_{x=1}^{W}\sum_{y=1}^{H}\overline{U}_{x,y}(P)
  \ .
\end{equation}
In this specific experiment, $W=2000$, $H=2000$ and $n=19$. The $F$ statistic is
\begin{equation}
F(P)=\dfrac{s_\mathrm{b}^2(P)}{s_\mathrm{w}^2(P)}
\end{equation}
and it should be about one if the within and between pixel variances are similar. The experiment was repeated 100 times by reallocating the training and test set.

@@

Using the $F$ test from ANOVA was found to be too strict in this experiment. Under the hypothesis that the grey values all have the same mean and assume they are Normally distributed and i.i.d., then $F(P)\sim F_{WH-1, WH(n-1)}$. In this experiment, the 5\% critical value is 1.001 to 3 decimal places, this is too small for this analysis. This may be due to the grey values of the greyscale projections not satisfying the assumptions for the $F$ test, for example, they may not be i.i.d.

>>>>

For each power, the within and between pixel variance was calculated. Let $U_{x,y}^{(j)}(P)$ be the shading corrected greyscale image in the test set with power $P$ for $j=1,2,\dotsc,m$ replicates. The within and between pixel variance are
\begin{equation}
s_\mathrm{w}^2(P)=\dfrac{1}{WH(m-1)}
  \sum_{x=1}^{W}\sum_{y=1}^{H}\sum_{j=1}^{m}
  \left(
    U_{x,y}^{(j)}(P) - \overline{U}_{x,y}(P)
  \right)^2
\end{equation}
and
\begin{equation}
s_\mathrm{b}^2(P)=\dfrac{m}{WH-1}
  \sum_{x=1}^{W}\sum_{y=1}^{H}
  \left(
    \overline{U}_{x,y}(P) - \overline{U}(P)
  \right)^2
\end{equation}
respectively where
\begin{equation}
  \overline{U}_{x,y}(P) = \dfrac{1}{m}\sum_{j=1}^{m}U_{x,y}^{(j)}(P)
\end{equation}
and
\begin{equation}
  \overline{U}(P) = \dfrac{1}{WH}\sum_{x=1}^{W}\sum_{y=1}^{H}\overline{U}_{x,y}(P)
  \ .
\end{equation}
In this specific experiment, $W=2000$, $H=2000$ and $m=19$. The $F$ statistic is
\begin{equation}
F(P)=\dfrac{s_\mathrm{b}^2(P)}{s_\mathrm{w}^2(P)}
\end{equation}
and it should be about one if the within and between pixel variances are similar. The experiment was repeated 100 times by reallocating the training and test set.

@@

Using the $F$ test from ANOVA was found to be too strict in this experiment. Under the hypothesis that the grey values all have the same mean and assume they are Normally distributed and i.i.d., then $F(P)\sim F_{WH-1, WH(m-1)}$. In this experiment, the 5\% critical value is 1.001 to 3 decimal places, this is too small for this analysis. This may be due to the grey values of the greyscale projections not satisfying the assumptions for the $F$ test, for example, they may not be i.i.d.

### 2019-09-15 reports/thesis/chapters/3_compoundPoisson.tex
Change notation

The compound Poisson-gamma distribution can be used to model the grey value of each pixel in a projection. Suppose a projection has $m$ pixels and $n$ replicate projections were obtained. Let $X_{i,j}$ and $Y_{i,j}$ be the grey value and photon count, respectively, of the $i$th pixel in the $j$th replicate projection.

@@

The model may be simplified by omitting the electronic noise and this can be done by setting $a=0$ and $\kappa=0$. The number of pixels can be set to $m=1$ to simplify the model further. Parameter estimation can be done using gradient methods because the likelihood of the compound Poisson can be evaluated \citep{dunn2005series}. However, the EM algorithm is faster and the model is well set up for it.

>>>>

The compound Poisson-gamma distribution can be used to model the grey value of each pixel in a projection. Suppose a projection has $N$ pixels and $m$ replicate projections were obtained. Let $X_{i,j}$ and $Y_{i,j}$ be the grey value and photon count, respectively, of the $i$th pixel in the $j$th replicate projection.

@@

The model may be simplified by omitting the electronic noise and this can be done by setting $a=0$ and $\kappa=0$. The number of pixels can be set to $N=1$ to simplify the model further. Parameter estimation can be done using gradient methods because the likelihood of the compound Poisson can be evaluated \citep{dunn2005series}. However, the EM algorithm is faster and the model is well set up for it.

### 2019-09-15 reports/thesis/chapters/4_variancePrediction.tex
Change notation

The sample variance-mean data were obtained from the replicate projections. Let $x_{i,j}^{(r)}$ be the grey value of the pixel at $(i,j)$ from the $r$th replicate projection for $r=1,2,3,\dotsc,n$. The sample mean and sample variance grey value for the pixel at $(i,j)$ are
\begin{equation}
    \overline{x}_{i,j}=\frac{1}{n}\sum_{r=1}^n x_{i,j}^{(r)}
\end{equation}
and
\begin{equation}
    y_{i,j} =
    \frac{1}{n-1}
    \sum_{r=1}^n
        \left(
            x_{i,j}^{(r)} - \overline{x}_{i,j}
        \right)^2
\end{equation}
respectively. Only pixels in the region of interest (ROI) were considered here, that is, pixels which represent the test sample. The ROI was created by manually segmenting the test sample from the projection.

The aim is to model and predict the grey value variance of a pixel given the pixel's grey value by using a model fitted onto the sample variance-mean data. No spatial information was used, thus, the variance-mean data is denoted as $(x_1,y_1),(x_2,y_2),\dotsc,(x_m,y_m)$ from now on, where $m$ is the area of the ROI or the size of the dataset. Let $Y(x)$ be a random variable and the sample variance given a grey value mean $x$. It was assumed that the standard error from estimating the mean was negligible so that the uncertainty is captured by the random variable $Y$. It was assumed that for a given pixel, the grey values are Normal and i.i.d. Let $\sigma^2(x)$ be the variance given a grey value $x$, then it can be shown that
\begin{equation}
\dfrac{(n-1)Y(x)}{\sigma^2(x)}\sim\chi^2_{n-1}
\end{equation}
which results in
\begin{equation}
Y(x)\sim\gammaDist\left(\alpha,\dfrac{\alpha}{\sigma^2(x)}\right)
\end{equation}
where $\alpha=(n-1)/2$ is the shape parameter. The expectation and variance are
\begin{equation}
\expectation\left[Y(x)\right]=\sigma^2(x)
\end{equation}
and
\begin{equation}
\variance\left[Y(x)\right]=\dfrac{\sigma^2(x)}{\alpha}
\end{equation}
respectively.

@@

The AIC and BIC are given as
\begin{equation}
\AIC = 2k-2\ln L
\end{equation}
and
\begin{equation}
\BIC = k\ln m - 2\ln L
\end{equation}
respectively where $k$ is the number of parameters in the systematic component and $\ln L$ is the log-likelihood of the GLM. The model with the lowest AIC or BIC is preferred. GLM aims to maximise the log-likelihood but the additional terms in the criteria penalise models with too many terms. The log-likelihood is given as
\begin{equation}
  \ln L = \sum_{i=1}^m \left[
    \alpha\ln\alpha
    -\ln\Gamma(\alpha)
    -\alpha\ln \widehat{y}_i
    +(\alpha-1)\ln y_i
    -\frac{\alpha y_i}{\widehat{y}_i}
  \right]
  \ .
\end{equation}
where $\widehat{y}_i=\widehat{y}(x_i)$. $\alpha=(n-1)/2$ was assumed to be known so does not need to be estimated.

@@

The mean scaled deviance was used to assess the performance of variance prediction. The deviance is defined to be
\begin{equation}
  D = 2\left(
    \ln L_\mathrm{s} - \ln L    
  \right)
\end{equation}
where $L$ and $L_\mathrm{s}$ are the likelihood and saturated likelihood respectively.  The saturated likelihood is obtained by replacing all $\widehat{y}_i$ with $y_i$ in the likelihood so that
\begin{equation}
  \ln L_\mathrm{s} = \sum_{i=1}^m \left[
    \alpha\ln\alpha
    -\ln\Gamma(\alpha)
    -\alpha\ln{y_i}
    +(\alpha-1)\ln y_i
    -\alpha
  \right]
  \ .
\end{equation}
Following from this, the deviance is
\begin{equation}
  D = 2\alpha
  \sum_{i=1}^m\left[
      \dfrac{
          y_i-\widehat{y}_i
      }
      {
          \widehat{y}_i
      }
      - \ln\left(\dfrac{y_i}{\widehat{y}_i}\right)
  \right]
  \ .
\end{equation}
The mean scaled deviance is obtained by removing the factor of $\alpha$ and dividing by $m$ to get
\begin{equation}
    D_\mathrm{s} = \dfrac{2}{m}
    \sum_{i=1}^m\left[
        \dfrac{
            y_i-\widehat{y}_i
        }
        {
            \widehat{y}_i
        }
        - \ln\left(\dfrac{y_i}{\widehat{y}_i}\right)
    \right]
    \ .
\end{equation}

@@

Assuming the model is correct, it is given that $D\sim\chi_{m-k}^2$ which implies that for large $m$,
\begin{equation}
\expectation\left[D_\mathrm{s}\right] = \dfrac{1}{\alpha}
\end{equation}
and
\begin{equation}
\variance\left[D_\mathrm{s}\right] = \dfrac{2}{\alpha^2 m} \ .
\end{equation}
Because $\alpha=(n-1)/2$, this shows that the number of replicated projections used to obtain the sample variance-mean data has an influence on the mean scaled deviance. This result can be used to estimate $\alpha$ if it is unknown.

>>>>

The sample variance-mean data were obtained from the replicate projections. Let $x_{i,j}^{(r)}$ be the grey value of the pixel at $(i,j)$ from the $r$th replicate projection for $r=1,2,3,\dotsc,m$. The sample mean and sample variance grey value for the pixel at $(i,j)$ are
\begin{equation}
    \overline{x}_{i,j}=\frac{1}{m}\sum_{r=1}^m x_{i,j}^{(r)}
\end{equation}
and
\begin{equation}
    y_{i,j} =
    \frac{1}{m-1}
    \sum_{r=1}^m
        \left(
            x_{i,j}^{(r)} - \overline{x}_{i,j}
        \right)^2
\end{equation}
respectively. Only pixels in the region of interest (ROI) were considered here, that is, pixels which represent the test sample. The ROI was created by manually segmenting the test sample from the projection.

The aim is to model and predict the grey value variance of a pixel given the pixel's grey value by using a model fitted onto the sample variance-mean data. No spatial information was used, thus, the variance-mean data is denoted as $(x_1,y_1),(x_2,y_2),\dotsc,(x_N,y_N)$ from now on, where $N$ is the area of the ROI or the size of the dataset. Let $Y(x)$ be a random variable and the sample variance given a grey value mean $x$. It was assumed that the standard error from estimating the mean was negligible so that the uncertainty is captured by the random variable $Y$. It was assumed that for a given pixel, the grey values are Normal and i.i.d. Let $\sigma^2(x)$ be the variance given a grey value $x$, then it can be shown that
\begin{equation}
\dfrac{(m-1)Y(x)}{\sigma^2(x)}\sim\chi^2_{m-1}
\end{equation}
which results in
\begin{equation}
Y(x)\sim\gammaDist\left(\alpha,\dfrac{\alpha}{\sigma^2(x)}\right)
\end{equation}
where $\alpha=(m-1)/2$ is the shape parameter. The expectation and variance are
\begin{equation}
\expectation\left[Y(x)\right]=\sigma^2(x)
\end{equation}
and
\begin{equation}
\variance\left[Y(x)\right]=\dfrac{\sigma^2(x)}{\alpha}
\end{equation}
respectively.

@@

The AIC and BIC are given as
\begin{equation}
\AIC = 2k-2\ln L
\end{equation}
and
\begin{equation}
\BIC = k\ln m - 2\ln L
\end{equation}
respectively where $k$ is the number of parameters in the systematic component and $\ln L$ is the log-likelihood of the GLM. The model with the lowest AIC or BIC is preferred. GLM aims to maximise the log-likelihood but the additional terms in the criteria penalise models with too many terms. The log-likelihood is given as
\begin{equation}
  \ln L = \sum_{i=1}^N \left[
    \alpha\ln\alpha
    -\ln\Gamma(\alpha)
    -\alpha\ln \widehat{y}_i
    +(\alpha-1)\ln y_i
    -\frac{\alpha y_i}{\widehat{y}_i}
  \right]
  \ .
\end{equation}
where $\widehat{y}_i=\widehat{y}(x_i)$. $\alpha=(m-1)/2$ was assumed to be known so does not need to be estimated.

@@

The mean scaled deviance was used to assess the performance of variance prediction. The deviance is defined to be
\begin{equation}
  D = 2\left(
    \ln L_\mathrm{s} - \ln L    
  \right)
\end{equation}
where $L$ and $L_\mathrm{s}$ are the likelihood and saturated likelihood respectively.  The saturated likelihood is obtained by replacing all $\widehat{y}_i$ with $y_i$ in the likelihood so that
\begin{equation}
  \ln L_\mathrm{s} = \sum_{i=1}^N \left[
    \alpha\ln\alpha
    -\ln\Gamma(\alpha)
    -\alpha\ln{y_i}
    +(\alpha-1)\ln y_i
    -\alpha
  \right]
  \ .
\end{equation}
Following from this, the deviance is
\begin{equation}
  D = 2\alpha
  \sum_{i=1}^N\left[
      \dfrac{
          y_i-\widehat{y}_i
      }
      {
          \widehat{y}_i
      }
      - \ln\left(\dfrac{y_i}{\widehat{y}_i}\right)
  \right]
  \ .
\end{equation}
The mean scaled deviance is obtained by removing the factor of $\alpha$ and dividing by $N$ to get
\begin{equation}
    D_\mathrm{s} = \dfrac{2}{N}
    \sum_{i=1}^N\left[
        \dfrac{
            y_i-\widehat{y}_i
        }
        {
            \widehat{y}_i
        }
        - \ln\left(\dfrac{y_i}{\widehat{y}_i}\right)
    \right]
    \ .
\end{equation}

@@

Assuming the model is correct, it is given that $D\sim\chi_{N-k}^2$ which implies that for large $N$,
\begin{equation}
\expectation\left[D_\mathrm{s}\right] = \dfrac{1}{\alpha}
\end{equation}
and
\begin{equation}
\variance\left[D_\mathrm{s}\right] = \dfrac{2}{\alpha^2 N} \ .
\end{equation}
Because $\alpha=(m-1)/2$, this shows that the number of replicated projections used to obtain the sample variance-mean data has an influence on the mean scaled deviance. This result can be used to estimate $\alpha$ if it is unknown.

### 2019-09-15 reports/thesis/chapters/5_inference.tex
Change notation

A disagreement between the obtained and the \emph{aRTist} simulated projections can be found by subtracting one projection from the other. Any values too big in magnitude can be considered as a defect. However, in the previous chapters, it was found that x-ray photons behave randomly and differences in the comparison can be due to chance. Thus, the comparisons should be done in the face of uncertainty.

A pixel by pixel hypothesis test was proposed to do defect detection. The test statistic, for the pixel located at $(x,y)$, is
\begin{equation}
  Z_{x,y} = 
  \dfrac{
    \text{projection}_{x,y} - \emph{aRTist}_{x,y}
  }
  {
    \sqrt{\widehat{\variance}\left[\text{projection}_{x,y}\right]}
  }
\end{equation}
where $\widehat{\variance}\left[\text{projection}_{x,y}\right]$ is the estimated grey value variance. The test statistic was calculated for each pixel in the projection. For high photon rate, it was shown in the previous chapters that the grey values in the scan can be modelled using a Normal distribution. Thus, if there are no significant differences between the obtained and \emph{aRTist} projections, then the randomness of the test statistics can be approximately quantified as
\begin{equation}
Z_{x,y}\sim \normal(0,1) \ .
\end{equation}
As with usual statistical convention, an upper case $Z$ denotes a random variable. A lower case $z$ denotes a realisation or an observation of that random variable.

@@

Multiple hypotheses testing occurs when there are more than one hypotheses to test. For example, $n$ pixels can be tested where the test statistics are $Z_1, Z_2, \dotsc, Z_n$ and $Z_i\sim\normal(\mu_i,1)$ for $i=1,2,\dotsc,n$. The null hypotheses are $H_{0,i}:\mu_i=0$ and are tested against the alternative $H_{1,i}:\mu_i\neq 0$ for $i=1,2,\dotsc,n$. Let the corresponding $p$-values be $p_1, p_2, \dotsc, p_n$.

The uncorrected test classify any $p_i<\alpha$ as positive. This is flawed because the possibility of obtaining at least one false positive increases as the number of tests increases \citep{shaffer1995multiple}. This method does control the per comparison error rate (PCER) \citep{benjamini1995controlling}. PCER is the proportion of false positives out of all tests. The notation for the number of true/false positive/negatives obtained are defined in Table \ref{table:inference_randomvariables}. Using the notation, the PCER is defined as
\begin{equation}
  \text{PCER}=
  \dfrac{1}{n}
  \expectation[V]
  \ .
\end{equation}
It can be seen that if the uncorrected test controls the false positive rate such that $\expectation[V]/n_0 = \alpha$, then it controls the PCER such that
\begin{equation}
  \text{PCER}\leqslant\alpha \ .
\end{equation}

\begin{table}
  \centering
  \begin{tabular}{c|c|c|c}
    &Negative&Positive&Total\\\hline
    Null & $U$ & $V$ & $n_0$\\
    Non-null & $T$ & $S$ & $n-n_0$\\\hline
    &$n-R$&$R$&$n$
  \end{tabular}
  \caption{Random variable definitions for the number of true/false positives/negatives made in multiple hypotheses testing}
  \label{table:inference_randomvariables}
\end{table}

The Bonferroni correction \citep{shaffer1995multiple, bland1995multiple, perneger1998what} controls the family-wise error rate (FWER) \citep{shaffer1995multiple} where
\begin{equation}
  \text{FWER} = \prob(V\geqslant1) \ .
  \label{eq:inference_fwer}
\end{equation}
This is done by adjusting the size of the test to be $\alpha/n$. By using the adjusted size, then $\text{FWER}=1-\left[(1-\alpha/n)^n\right]$. Using the approximation $(1-\alpha/n)^n\approx 1-\alpha$ then $\text{FWER}\approx \alpha$. This shows that the Bonferroni correction controls the family-wise error rate such that
\begin{equation}
  \text{FWER} \leqslant \alpha \ .
\end{equation}
In practice, the Bonferroni correction is not very powerful \citep{perneger1998what}, meaning it gives too many false negatives. This is because the correction traded too many false positives for false negatives.

@@

The BH procedure adjusts the size of the test between the Bonferroni correction and the uncorrected test. It adapts to the data and chooses different sizes for different data. The procedure is as follows, the $p$-values are ordered such that $p_{(1)}\leqslant p_{(2)}\leqslant \dotsc \leqslant p_{(n)}$. Suppose a size $\alpha$ is provided beforehand. The size is adjusted to
\begin{equation}
  \alpha_{\text{BH}} = \frac{\alpha k}{n}
\end{equation}
where
\begin{equation}
  k\text{ is the largest }i\text{ for which }p_{(i)}\leqslant\frac{i}{n}\alpha
  \ .
\end{equation}
This test the statistics with $p$-values $p_{(1)},p_{(2)},\dotsc,p_{(k)}$ as positive. For the case where $p_{(1)}>\alpha/n$ then $k=1$ so that the Bonferroni correction is used when there are no positive results, this is only for illustration purposes. For example in Figure \ref{fig:inference_inferenceIntro_pvalue}, the $p$-values were plotted against their order so that the critical boundary was shown by a linear curve with gradient $\alpha/n$.

@@

In practice $\mu_0$ and $\sigma_0$ are unknown. The empirical null \citep{efron2004large} replaces the parameters of the null distribution with its estimate. Suppose $\widehat{\mu}_0$ and $\widehat{\sigma}_0$ are the estimated null mean and null standard deviation respectively. The statistics are specified by $Z_i\sim\normal(\mu_i, \widehat{\sigma}_0^2)$ so that the following null hypotheses $H_{0,i}:\mu_i=\widehat{\mu}_0$ are tested against $H_{1,i}:\mu_i\neq\widehat{\mu}_0$ for $i=1,2,\dotsc,n$.

@@

Returning back to the sub-image example in Figure \ref{fig:inference_inferenceSubsample1_histogram}. The histogram was smoothed using a kernel density estimate \citep{parzen1962on, friedman2001elements} as shown in Figure \ref{fig:inference_inferenceSubsample1_densityEstimate}. The kernel density estimate \citep{parzen1962on} is
\begin{equation}
  \widehat{p}_Z(z)=
  \frac{1}{nh}
  \sum_{i=1}^n\phi\left(
    \dfrac{z_i-z}{h}
  \right)
  \label{eq:inference_kernel_density_estimate}
\end{equation}
where $h$ is the bandwidth and $\phi(x)$ is the standard Normal density. The bandwidth was chosen such that
\begin{equation}
  h = (0.9n^{-1/5}\ + 0.16) \times \text{min}\left(s_z,\text{IQR}_z/1.34\right)
  \label{eq:inference_ourruleofthumb}
\end{equation}
where $s_z$ and $\text{IQR}_z$ are the sample standard deviation and sample interquartile range. This bandwidth is justified later on in this section.

@@

The test statistics were normalised to $T_1,T_2,\dotsc,T_n$ by using
\begin{equation}
  T_i = \dfrac{
    Z_i - \widehat{\mu}_0
  }
  {
    \widehat{\sigma}_0
  }
  \label{eq:inference_empiricalNullNormalise}
\end{equation}
for $i=1,2,\dotsc,n$. The normalised $p$-values were obtained by using
\begin{equation}
  p_i = 2(1-\Phi(|t_i|))
\end{equation}
and were used in the BH procedure. The critical region was found to be $|t|\geqslant\inputNumber{../figures/inference/inferenceSubsample1_nullNormalisedCritical.txt}$. In terms of the original units, the critical region was $z \leqslant \inputNumber{../figures/inference/inferenceSubsample1_nullCritical1.txt}$ and $\inputNumber{../figures/inference/inferenceSubsample1_nullCritical2.txt}\leqslant z$, all to 2 decimal places. The critical region and the normalised $p$-values are shown in Figure \ref{fig:inference_inferenceSubsample1_nullResults}.

@@

The empirical null filter uses the empirical null on neighbouring pixels to estimate the null parameters. To estimate $\mu_{0,x,y}$ and $\sigma_{0,x,y}$, a circular kernel $C_r(x,y)$ of radius $r$ was centred at $(x,y)$. All the pixels captured by the circular kernel and the ROI were used for the empirical null to obtain $\widehat{\mu}_{0,x,y}$ and $\widehat{\sigma}_{0,x,y}$, in other words
\begin{equation}
  \widehat{\mu}_{0,x,y} = \argmax\widehat{p}_{Z_{x,y}}(z)
\end{equation}
\begin{equation}
  \widehat{\sigma}_{0,x,y} = \left[
    \left.
      -\dfrac{\partial^2}{\partial z^2}\ln\widehat{p}_{Z_{x,y}}(z)
    \right|_{z=\widehat{\mu}_{0,x,y}}
  \right]^{-1/2}
\end{equation}
where
\begin{equation}
\widehat{p}_{Z_{x,y}}(z) = 
\frac{1}{nh}
  \sum_{i,j\in K_{x,y}}\phi\left(
    \dfrac{z_{i,j}-z}{h}
  \right) \ ,
\end{equation}
$K_{x,y} = C_r(x,y) \cap \text{ROI}$ and $n=\left|K_{x,y}\right|$. Using these estimates, the test statistics were normalised using
\begin{equation}
  T_{x,y} = 
  \dfrac{
    Z_{x,y}-\widehat{\mu}_{0,x,y}
  }
  {
    \widehat{\sigma}_{0,x,y}
  }
\end{equation}
and only the normalised test statistics were used in hypotheses testing. It should be noted that because the kernels can overlap, correlation between $T_{x,y}$ for different $(x,y)$ is introduced.

>>>>

Disagreements between the obtained and the \emph{aRTist} simulated projections can be found by subtracting one projection from the other. Any values too big in magnitude can be considered as a defect. However, in the previous chapters, it was found that x-ray photons behave randomly and differences in the comparison can be due to chance. Thus, the comparisons should be done in the face of uncertainty.

A pixel by pixel hypothesis test was proposed to do defect detection. The test statistic, for the pixel located at $(x,y)$, is
\begin{equation}
  Z_{x,y} = 
  \dfrac{
    \text{projection}_{x,y} - \emph{aRTist}_{x,y}
  }
  {
    \sqrt{\widehat{\variance}\left[\text{projection}_{x,y}\right]}
  }
\end{equation}
where $\widehat{\variance}\left[\text{projection}_{x,y}\right]$ is the estimated grey value variance. The test statistic was calculated for each pixel in the ROI, that is, pixels which represent the test sample. The ROI was created by manually segmenting the test sample from the projection.

For high photon rate, it was shown in the previous chapters that the grey values in the scan can be modelled using a Normal distribution. Thus, if there are no significant differences between the obtained and \emph{aRTist} projections, then the randomness of the test statistics can be approximately quantified as
\begin{equation}
Z_{x,y}\sim \normal(0,1) \ .
\end{equation}
As with usual statistical convention, an upper case $Z$ denotes a random variable. A lower case $z$ denotes a realisation or an observation of that random variable.

@@

Multiple hypotheses testing occurs when there are more than one hypotheses to test. For example, $N$ pixels can be tested where the test statistics are $Z_1, Z_2, \dotsc, Z_N$ and $Z_i\sim\normal(\mu_i,1)$ for $i=1,2,\dotsc,N$. The null hypotheses are $H_{0,i}:\mu_i=0$ and are tested against the alternative $H_{1,i}:\mu_i\neq 0$ for $i=1,2,\dotsc,N$. Let the corresponding $p$-values be $p_1, p_2, \dotsc, p_N$.

The uncorrected test classify any $p_i<\alpha$ as positive. This is flawed because the possibility of obtaining at least one false positive increases as the number of tests increases \citep{shaffer1995multiple}. This method does control the per comparison error rate (PCER) \citep{benjamini1995controlling}. PCER is the proportion of false positives out of all tests. The notation for the number of true/false positive/negatives obtained are defined in Table \ref{table:inference_randomvariables}. Using the notation, the PCER is defined as
\begin{equation}
  \text{PCER}=
  \dfrac{1}{N}
  \expectation[V]
  \ .
\end{equation}
It can be seen that if the uncorrected test controls the false positive rate such that $\expectation[V]/N_0 = \alpha$, then it controls the PCER such that
\begin{equation}
  \text{PCER}\leqslant\alpha \ .
\end{equation}

\begin{table}
  \centering
  \begin{tabular}{c|c|c|c}
    &Negative&Positive&Total\\\hline
    Null & $U$ & $V$ & $N_0$\\
    Non-null & $T$ & $S$ & $N-N_0$\\\hline
    &$N-R$&$R$&$N$
  \end{tabular}
  \caption{Random variable definitions for the number of true/false positives/negatives made in multiple hypotheses testing}
  \label{table:inference_randomvariables}
\end{table}

The Bonferroni correction \citep{shaffer1995multiple, bland1995multiple, perneger1998what} controls the family-wise error rate (FWER) \citep{shaffer1995multiple} where
\begin{equation}
  \text{FWER} = \prob(V\geqslant1) \ .
  \label{eq:inference_fwer}
\end{equation}
This is done by adjusting the size of the test to be $\alpha/N$. By using the adjusted size, then $\text{FWER}=1-\left[(1-\alpha/N)^N\right]$. Using the approximation $(1-\alpha/N)^N\approx 1-\alpha$ then $\text{FWER}\approx \alpha$. This shows that the Bonferroni correction controls the family-wise error rate such that
\begin{equation}
  \text{FWER} \leqslant \alpha \ .
\end{equation}
In practice, the Bonferroni correction is not very powerful \citep{perneger1998what}, meaning it gives too many false negatives. This is because the correction traded too many false positives for false negatives.

@@

The BH procedure adjusts the size of the test between the Bonferroni correction and the uncorrected test. It adapts to the data and chooses different sizes for different data. The procedure is as follows, the $p$-values are ordered such that $p_{(1)}\leqslant p_{(2)}\leqslant \dotsc \leqslant p_{(N)}$. Suppose a size $\alpha$ is provided beforehand. The size is adjusted to
\begin{equation}
  \alpha_{\text{BH}} = \frac{\alpha k}{N}
\end{equation}
where
\begin{equation}
  k\text{ is the largest }i\text{ for which }p_{(i)}\leqslant\frac{i}{N}\alpha
  \ .
\end{equation}
This test the statistics with $p$-values $p_{(1)},p_{(2)},\dotsc,p_{(k)}$ as positive. For the case where $p_{(1)}>\alpha/N$ then $k=1$ so that the Bonferroni correction is used when there are no positive results, this is only for illustration purposes. For example in Figure \ref{fig:inference_inferenceIntro_pvalue}, the $p$-values were plotted against their order so that the critical boundary was shown by a linear curve with gradient $\alpha/N$.

@@

In practice $\mu_0$ and $\sigma_0$ are unknown. The empirical null \citep{efron2004large} replaces the parameters of the null distribution with its estimate. Suppose $\widehat{\mu}_0$ and $\widehat{\sigma}_0$ are the estimated null mean and null standard deviation respectively. The statistics are specified by $Z_i\sim\normal(\mu_i, \widehat{\sigma}_0^2)$ so that the following null hypotheses $H_{0,i}:\mu_i=\widehat{\mu}_0$ are tested against $H_{1,i}:\mu_i\neq\widehat{\mu}_0$ for $i=1,2,\dotsc,N$.

@@

Returning back to the sub-image example in Figure \ref{fig:inference_inferenceSubsample1_histogram}. The histogram was smoothed using a kernel density estimate \citep{parzen1962on, friedman2001elements} as shown in Figure \ref{fig:inference_inferenceSubsample1_densityEstimate}. The kernel density estimate \citep{parzen1962on} is
\begin{equation}
  \widehat{p}_Z(z)=
  \frac{1}{nh}
  \sum_{i=1}^n\phi\left(
    \dfrac{z_i-z}{h}
  \right)
  \label{eq:inference_kernel_density_estimate}
\end{equation}
where $h$ is the bandwidth, $\phi(x)$ is the standard Normal density and $n=N$ is number of terms in the summation. The bandwidth was chosen such that
\begin{equation}
  h = (0.9n^{-1/5}\ + 0.16) \times \text{min}\left(s_z,\text{IQR}_z/1.34\right)
  \label{eq:inference_ourruleofthumb}
\end{equation}
where $s_z$ and $\text{IQR}_z$ are the sample standard deviation and sample interquartile range. This bandwidth is justified later on in this section.

@@

The test statistics were normalised to $T_1,T_2,\dotsc,T_N$ by using
\begin{equation}
  T_i = \dfrac{
    Z_i - \widehat{\mu}_0
  }
  {
    \widehat{\sigma}_0
  }
  \label{eq:inference_empiricalNullNormalise}
\end{equation}
for $i=1,2,\dotsc,N$. The normalised $p$-values were obtained by using
\begin{equation}
  p_i = 2(1-\Phi(|t_i|))
\end{equation}
and were used in the BH procedure. The critical region was found to be $|t|\geqslant\inputNumber{../figures/inference/inferenceSubsample1_nullNormalisedCritical.txt}$. In terms of the original units, the critical region was $z \leqslant \inputNumber{../figures/inference/inferenceSubsample1_nullCritical1.txt}$ and $\inputNumber{../figures/inference/inferenceSubsample1_nullCritical2.txt}\leqslant z$, all to 2 decimal places. The critical region and the normalised $p$-values are shown in Figure \ref{fig:inference_inferenceSubsample1_nullResults}.

@@

The empirical null filter uses the empirical null on neighbouring pixels to estimate the null parameters. To estimate $\mu_{0,x,y}$ and $\sigma_{0,x,y}$, a circular kernel $C_r(x,y)$ of radius $r$ was centred at $(x,y)$. All the pixels captured by the circular kernel and the ROI were used for the empirical null to obtain $\widehat{\mu}_{0,x,y}$ and $\widehat{\sigma}_{0,x,y}$, in other words
\begin{equation}
  \widehat{\mu}_{0,x,y} = \argmax\widehat{p}_{Z_{x,y}}(z)
\end{equation}
\begin{equation}
  \widehat{\sigma}_{0,x,y} = \left[
    \left.
      -\dfrac{\partial^2}{\partial z^2}\ln\widehat{p}_{Z_{x,y}}(z)
    \right|_{z=\widehat{\mu}_{0,x,y}}
  \right]^{-1/2}
\end{equation}
where
\begin{equation}
\widehat{p}_{Z_{x,y}}(z) = 
\frac{1}{nh}
  \sum_{i,j\in K_{x,y}}\phi\left(
    \dfrac{z_{i,j}-z}{h}
  \right) \ ,
\end{equation}
$K_{x,y} = C_r(x,y) \cap \text{ROI}$ and $n=\left|K_{x,y}\right|$, not to be confused with $N$. A bandwidth of $h = (0.9n^{-1/5}\ + 0.16) \times \text{min}\left(s_{x,y},\text{IQR}_{x,y}/1.34\right)$ was used where $s_{x,y}$ and $\text{IQR}_{x,y}$ are the sample standard deviation and sample interquartile range of the test statistics in $K_{x,y}$.

After obtaining the estimates of the empirical null parameters, the test statistics were normalised using
\begin{equation}
  T_{x,y} = 
  \dfrac{
    Z_{x,y}-\widehat{\mu}_{0,x,y}
  }
  {
    \widehat{\sigma}_{0,x,y}
  }
\end{equation}
and only the normalised test statistics were used in hypotheses testing. It should be noted that because the kernels can overlap, correlation between $T_{x,y}$ for different $(x,y)$ is introduced.
